### 2013-09-18 chi2014/results.tex
Fixed plots

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{ideas_over_time}
    \caption{Cumulative idea count}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\columnwidth]{rate_new_idea_over_time}
    \includegraphics[width=0.7\columnwidth]{rate_new_category_over_time}
    \includegraphics[width=0.7\columnwidth]{rate_new_ns_category_over_time}
    \caption{Rate of idea generation}
\end{figure}

@@

\subsubsection{Originality of Ideas}
Complementing the view of what ideas are generated when, we now consider idea and idea category o-scores as a function of response number. This analysis allows us to examine hypothesis 4, or our expectation that o-scores increase as a function of response number.

Test here...

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{cumulative_ideas}
    \caption{Cumulative number of novel ideas}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{cumulative_categories}
    \caption{Cumulative number of novel idea categories}
\end{figure}

% \begin{figure}[h!]
%     \centering
%     \includegraphics[width=0.7\columnwidth]{rate_new_idea_over_time}
%     \includegraphics[width=0.7\columnwidth]{rate_new_category_over_time}
%     \includegraphics[width=0.7\columnwidth]{rate_new_ns_category_over_time}
%     \caption{Rate of idea generation}
% \end{figure}

@@

\subsubsection{Originality of Ideas}
Complementing the view of what ideas are generated when, we now consider idea and idea category o-scores as a function of response number. This analysis allows us to examine hypothesis 4, or our expectation that o-scores increase as a function of response number. We examine o-scores for both ideas and idea categories.
